# Using the R caret package for Machine Learning 

Load caret and kernlab packages. Load the spam dataset. 
```{r}
library(caret)
library(kernlab)
data(spam)
```

Create a training data set using 75% of the spam dataset, leaving 25% of the spam dataset for the testing set. 
```{r}
inTrain <- createDataPartition(y=spam$type, p=0.75, list=FALSE)
training <- spam[inTrain,]
testing <- spam[-inTrain,]
dim(training)
```

Fit a Generalized Linear Model. There is linear separation which is why the "## Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred" happens. 
```{r}
set.seed(32343)
modelFit <- train(type ~., data=training, method="glm")
modelFit
```

Look at the final model. There is linear separation which is why the "## Warning: glm.fit: fitted probabilities numerically 0 or 1 occurred" happens. 
```{r}
modelFit <- train(type ~., data=training, method="glm")
modelFit$finalModel
```

Predict on new samples.
```{r}
predictions <- predict(modelFit, newdata=testing)
predictions
```

Evaluate model fit using a confusion matrix. 
```{r}
confusionMatrix(predictions, testing$type)
```





